---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/tmsalab/$PACKAGE$.svg)](https://travis-ci.org/tmsalab/$PACKAGE$)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
[![CRAN Version Badge](http://www.r-pkg.org/badges/version/$PACKAGE$)](https://cran.r-project.org/package=$PACKAGE$)
[![CRAN Status](https://cranchecks.info/badges/worst/$PACKAGE$)](https://cran.r-project.org/web/checks/check_results_$PACKAGE$.html)
[![RStudio CRAN Mirror's Monthly Downloads](http://cranlogs.r-pkg.org/badges/$PACKAGE$?color=brightgreen)](http://www.r-pkg.org/pkg/$PACKAGE$)
[![RStudio CRAN Mirror's Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/$PACKAGE$?color=brightgreen)](http://www.r-pkg.org/pkg/$PACKAGE$)
[![Coverage status](https://codecov.io/gh/tmsalab/$PACKAGE$/branch/master/graph/badge.svg)](https://codecov.io/github/tmsalab/$PACKAGE$?branch=master)

# `$PACKAGE$` R package

What does the package do? 

## Installation

You can install `$PACKAGE$` from CRAN using:

```{r cran-installation, eval = FALSE}
install.packages("$PACKAGE$")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r gh-installation, eval = FALSE}
if(!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("tmsalab/$PACKAGE$")
```

## Usage

To use the `$PACKAGE$` package, load it into _R_ using:

```{r example, message = FALSE, eval = FALSE}
library("$PACKAGE$")
```

From there, the package allows for ....


## Authors

Who wrote the package? 

## Citing the `$PACKAGE$` package

To ensure future development of the package, please cite `$PACKAGE$`
package if used during an analysis or simulation studies. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("$PACKAGE$")
```

## License

GPL (>= 2)
